Structuring College Access

### 2025-02-15 index.qmd
remove test slide
start revising presentation

College Board "Geomarkets"

- Carve states and metropolitan areas into smaller geographic regions meant to define local recruiting markets

Geomarkets are an input to two College Board products

- Enrollment Planning Service (est. 1984): software recommends which Geomarkets to recruit and which high schools to visit
- Student Search Service (est. 1972): purchase the contact information of prospects that meet "search filter" criteria

Research questions

1. What is SES, racial variation between, within Geomarkets? Over time?
1. What is SES and racial composition of included vs. excluded prospects, if student list purchases filter on particular Geomarkets?

Research interest: how quantification reproduces social stratification

@@

::: columns
::: {.column width="40%"}

<img src="./assets/images/nyc_geomarkets.png" data-width="60%">
:::

::: {.column width="60%"}

![](./assets/images/chicago_geomarkets.png)
:::
:::

@@

**Market Segment Model**, based on student SAT score-sending behavior

@@

@@

### Test map{.hide}

<iframe src="https://comforting-kashata-600ce0.netlify.app/" width=100% height=100% allowtransparency="true"></iframe>

>>>>

Historically, College Board offered two recruiting products to colleges

- Student Search Service (est. 1972): purchase contact information of prospects that meet "search filter" criteria
- Enrollment Planning Service (est. 1984): software-as-service, says which "Geomarkets" to target and which high schools to visit

College Board "Geomarkets" are an input in both products

- Geomarkets carve states and metro areas into smaller geographic regions meant to define local recruiting markets [@RN4982]

Concerns: Geomarket borders correlated with race/class; likely to be used in ways that undermine equality of opportunity

1. What is SES, racial variation between, within Geomarkets? Over time?
1. What is SES and racial composition of included vs. excluded prospects when student list purchases filter on particular Geomarkets?

<!-- Research interest: how quantification reproduces social stratification -->

@@

::: columns
::: {.column width="50%"}

![](./assets/images/chicago_geomarkets.png)

<!-- <img src="./assets/images/nyc_geomarkets.png" data-width="60%"> -->
:::

::: {.column width="50%"}
**[University of Chicago admissions counselors, Chicago-land](https://collegeadmissions.uchicago.edu/contact)**
![](./assets/images/chicagoland_territories_u_chicago_redacted.png)
:::
:::

@@

@@

**Market Segment Model**, based on student SAT score-sending behavior [SIMPLIFY]

@@
